Elements of meaningful data sharing

### 2021-03-29 new-paper.Rmd
re-add comment on privact concerns and the benefits of data sharing.

>>>>

Assuming that the data have no privacy concerns (e.g., human participants, locations of critically endangered species), or that the act of sharing does not put the authors at a competitive disadvantage (data can be embargoed for reasonable periods of time), sharing data will always have a net positive benefit.
